Hierarchical Dispatching and Overriding

### 2017-09-16 NewVersion/sections/TypeSafety.tex
2nd fix.

\subsubsection{Proof for Theorem~\ref{theorem_subject}}
\begin{proof} ~\\
\noindent\textcolor{red}{\textbf{Case PathInvk.} Let} \haoyuan{where to use lemma 1}
  $$\textcolor{red}{e = (\angl{J}\new{I}).K?m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}}$$
  $$\textcolor{red}{e' = \angl{I_e}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 \quad \judgeewf {\Gamma} {e' : I'_e}}$$
  $$\textcolor{red}{\mbody(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I_e \; e_0)}$$
\textcolor{red}{Since $e$ is well typed, $\angl{J}\new{I}$ is well typed, and}
  $$\textcolor{red}{\judgeewf {\Gamma} {\angl{J}\new{I} : I}}$$
\textcolor{red}{By \textsc{(T-Anno)}, we have $I \subtype J$.}

\noindent\textcolor{red}{Suppose that the original form of $(\angl{J}\new{I}).K?m(\overline{v})$ is $e_T.K?m(\overline{e_T})$ by reduction.
	The original expression should be type-checked already by \textsc{(T-PathInvk)}. Suppose that}
  $$\textcolor{red}{\judgeewf {\Gamma} {e_T : I_T} \quad \judgeewf {\Gamma} {\overline{e_T} : \overline{I_T}}}$$
\textcolor{red}{By induction hypothesis, $I \subtype I_T$. By lemma~\ref{lemma2_new},}
  $$\textcolor{red}{\mbody(m, I_T, K) = (\_, \overline{I_x}\ \_, I_e\ \_)}$$
\textcolor{red}{Therefore $\overline{I_T} \subtype \overline{I_x}$. By induction hypothesis,}
  $$\textcolor{red}{\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_T} \subtype \overline{I_x}}}$$
\textcolor{red}{So the first substitution preserves typing, On the other hand, .... the second one also preserves typing. Hence $I'_e \subtype$ type of $e_0 \subtype I_e$.}

>>>>

\subsubsection{Proof for Theorem~\ref{theorem_subject}}
\begin{proof} ~\\
\noindent\textcolor{red}{\textbf{Case PathInvk.} Let} \haoyuan{where to use lemma 1}
  $$\textcolor{red}{e = (\angl{J}\new{I}).K?m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}}$$
  $$\textcolor{red}{e' = \angl{I_e}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 \quad \judgeewf {\Gamma} {e' : I'_e}}$$
  $$\textcolor{red}{\mbody(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I_e \; e_0)}$$
\textcolor{red}{Since $e$ is well typed, $\angl{J}\new{I}$ is well typed, and}
  $$\textcolor{red}{\judgeewf {\Gamma} {\angl{J}\new{I} : I}}$$
\textcolor{red}{By \textsc{(T-Anno)}, we have $I \subtype J$. Also, by \textsc{(T-PathInvk)}, $\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_x}}$.}

\noindent \textcolor{red}{So the first substitution preserves typing, On the other hand, .... the second one also preserves typing. Hence $I'_e \subtype$ type of $e_0 \subtype I_e$.}
